---
title: "2025-2026 Help Desk Emergency Department Report"
format: pdf
editor: source
---

# Overview

```{r}
#| label: raceandinsurance
#| include: false
library(tidyverse)

#change dataset here Test
data <- read_csv("Data csv/Data 4:26:26.csv") 

firstSecond <- data |>
  filter(datescreen >= "2025-08-01" & datescreen < "2026-04-20")

thirdFourth <- data |>
  filter(datescreen >= "2023-8-01" & datescreen < "2025-08-01")

# date filter
data <- data |>
  filter(datescreen >= "2025-08-01" & datescreen < "2026-05-01")

data <- data |>
   mutate(race = if_else(race___0 == 1, 0, 
                         if_else(race___1 == 1, 1,
                                 if_else(race___2 == 1, 2,
                                         if_else(race___3 == 1, 3, 
                                                 if_else(race___4 == 1, 4,
                                                         if_else(race___5 == 1, 5,
                                                                 if_else(race___6 == 1, 6,
                                                                         if_else(race___7 == 1, 7, 0)))))))),
          .before = race___0)

data <- data |>
  mutate(race = if_else(race == 2 & hispanic == 0, 2, 
         if_else(race == 2 & hispanic == 1, 2.5,
                 if_else(race == 4 & hispanic == 0, 4,
                         if_else(race == 4 & hispanic == 1, 4.5,
                                 if_else(race != 2 & race != 4, race, -1))))))

data <- data |>
  mutate(insurance = if_else(insurance___1 == 1,
                             "Private Insurance",
                             if_else(insurance___2 == 2,
                                     "Medicaid",
                                     if_else(insurance___3 == 1,
                                             "Medicare",
                                             if_else(insurance___4 == 1,
                                                     "No Insurance",
                                                     if_else(insurance___5 == 1,
                                                             "Other",
                                                             "NA"))))))
```

```{r message=F, echo=F, warning=F}
#| label: convert race to text
#| include: false
data <- data |>
  mutate(race_txt = case_when(
    race == 0 ~ "Asian",
    race == 1 ~ "Pacific Islander",
    race == 2 ~ "White, Hispanic",
    race == 2.5 ~ "White, Not Hispanic",
    race == 3 ~ "Native Hawaiian",
    race == 4 ~ "Black, Hispanic",
    race == 4.5 ~ "Black, Not Hispanic",
    race == 5 ~ "American Indian/Alaskan Native",
    race == 6 ~ "No Answer",
    race == 7 ~ "Other",
  )) |>
  mutate(race_txt = fct_relevel(race_txt,
                                "Asian",
                                "American Indian/Alaskan Native",
                                "White, Hispanic",
                                "White, Not Hispanic",
                                "Black, Hispanic",
                                "Black, Not Hispanic",
                                "Pacific Islander",
                                "Native Hawaiian",
                                "No Answer",
                                "Other"))
```
```{r message=F, echo=F, warning=F}
#| label: number of patients 
#| include: false
# Each row in the csv is a patient who was screened. Number of patients talked to is not provided in csv.

#create followup 2 weeks_txt var
data <- data |>
  mutate(followup_2_weeks_complete_txt = case_when(
    followup_2_weeks_complete == 0 ~ "Incomplete",
    followup_2_weeks_complete == 1 ~ "Unverified",
    followup_2_weeks_complete == 2 ~ "Complete",
  ))

#scerened poitive
data <- data |>
  mutate(screened_positive = if_else(needs___9 == 0, "positive", "negative"))

# total num patients screened
total_patients <- data |>
  nrow()

# distinct patients screened
distinct_patients <- data |>
  distinct(duplicate_ck) |>
  nrow()

# screened positive
screened_pos <- data |>
  filter(screened_positive == "positive") |>
  nrow()

# wanted assistance
wanted_assis <- data |>
  filter(likeassistance == 1,
         screened_positive == "positive") |>
  nrow()

# number of referrals
num_referrals <- data |>
  filter(!is.na(attempt1_ref)) |>
  nrow()

# enrolled in nccare360
enrolled_nccare360 <- data |>
  filter(nccare360 == 1) |>
  nrow()

followup_comp <- data |>
  filter(followup_2_weeks_complete_txt == "Complete") |>
  nrow()
```

The 2025-2026 school year (defined by the dates of August 1st, 2025 to May 1st, 2026) saw `r total_patients` total screenings, with `r distinct_patients` distinct patients screened. `r screened_pos` patients screened positive for at least one need, and `r wanted_assis` patients wanted assistance with their needs. 

There were `r num_referrals` referrals given, with `r followup_comp` 2 week followups complete and `r enrolled_nccare360` patients enrolled in NCCARE360.


```{r message=F, echo=F, warning=F}
#| label: race breakdown
data |>
  count(race_txt) |>
  mutate(prop = round(n/sum(n) * 100, 1)) |>
  ggplot(aes(x = race_txt, y = prop)) +
  geom_bar(stat = "identity", fill = "lightblue", color = "black") +
  coord_flip(clip = "off") +
  theme_bw() +
  labs(x = "",
       y = "Percent",
       title = "Patient Breakdown By Race and Ethnicity",
       subtitle = "Who agreed to screening") +
  geom_text(aes(label = if_else(n < 20, "", paste("N =", n))), size = 3, hjust = 1.05) +
  geom_text(aes(label = if_else(n > 180, "", paste(prop, "%"))), hjust = -.3, size = 3) +
  geom_text(aes(label = if_else(n > 180, paste(prop, "%"), "")),
            hjust = 1,
            vjust = 4,
            size = 3)
                  
```




